R Script V5

### 2023-06-16 Data & Scripts/MSC R Script.Rmd
Another push
What I had on the desktop

@@

```{r Duration Histograms Individual, include = F}
Untransformed.Dur<-hist(Crow$Duration, breaks = 25)
Transformed.Dur<-hist(Crow$LDur, breaks = 25)
```

@@

```{r Crow Histogram, echo=F}
Hist<-ggplot(data = Crow) +
  geom_histogram(aes(fill = Behavior, x = LDur)
                 , alpha = 1
                 , bins = 50)+
  scale_fill_manual(values=cbPalette
                    , labels = c("Foraging", "Alert", "Moving"))+
  xlab("Log Duration (s)")+
  ylab("Count")
Hist
```

@@

### Boxplot

```{r Crow boxplot, echo = F}
Box<-ggplot(data = Crow)+
  geom_boxplot_pattern(aes(x = G.Env, y = LDur, fill = Behavior, pattern = Sentinel)
                       , pattern_angle = 45
                       , pattern_size = 0.05
                       , pattern_spacing = 0.02
                       , color = "black")+
  theme(legend.position = "bottom")+
  scale_fill_manual(values = cbPalette
                    , labels = c("Foraging", "Alert", "Moving"))+
  scale_pattern_manual(values = c("crosshatch", "none")
                       , labels = c("Sentinel Absent", "Sentinel Present"))+
  guides(pattern = guide_legend(title = "Presence of a sentinel"
                                , override.aes = list(fill = c("white")))
         , fill = guide_legend(override.aes = list(pattern = "none")))+
  xlab("Generalized Environment")+
  ylab("Log Duration(s)") +
  theme(axis.title.x = element_blank()
        , legend.position = "bottom"
        , legend.box="vertical"
        , legend.margin=margin())
Box
```

### Violin plot

```{r Crow Violin plot, echo = F}
Violin<-ggplot(data = Crow
               , aes(x = Behavior, y = LDur, fill = Sentinel))+
  geom_violin()+
  theme_bw()+
  theme(legend.position = "bottom")+
  scale_fill_manual(values = cbPalette
                    , labels = c("Sentinel Absent", "Sentinel Present"))+
  scale_x_discrete(labels=c("Foraging", "Alert", "Moving"))+
  xlab("Generalized Environment")+
  ylab("Log Duration(s)")+
  facet_grid(~G.Env)+
  stat_summary(fun = "mean"
               , geom = "crossbar"
               , position = "dodge"
               , color = "red")
Violin
```

>These plots are nice, but it is hard to really see the underlying trends. To best visualise them, I'll next plot a dot plot.

@@

```{r Base R Plot, include = F}
source("./Calculate Summary Table with SE, SD, CI by grouping variables.R")
MeanDur <- summarySE(data = Crow, measurevar = "Duration"
                     , groupvars = c("G.Env", "Behavior", "Sentinel"))

plot(x = c(1:12)
     , y = MeanDur$Duration
     , xlim = c(0,12)
     , ylim = c(1,3)
     , type = "n"
     , ylab = "Duration (seconds)", xlab = "Generalized Environment")
arrows(c(1:12), MeanDur$Duration - MeanDur$se
       , c(1:12), MeanDur$Duration + MeanDur$se
       , length = 0.1, angle = 90, code = 3, lwd = 2)
points(x = c(1:12), y = MeanDur$Duration
       , pch = c(rep(c(16, 17), 3)), cex = 2
       , col = c("orange", "orange", "blue", "blue", "green", "green"))
legend(x = "bottomright", c("Sentinel Absent", "Sentinal Present", "Foraging", "Alert", "Moving")
       , bty = "o", cex = 1.05, bg = "white"
       , pch = c(16, 17, 15, 15, 15), col = c("black", "black", "orange", "blue", "green"))
#KMG: I'm not going to fix the X-axis labels and those kinds of things right now. I can do that if you like this plot or things it's informative. I think it's easier to see the differences. left side is commercial, right side is green. Legend should be correct.
```

```{r Dot Plot V2, echo = F}
source("./Calculate Summary Table with SE, SD, CI by grouping variables.R")
MeanDur <- summarySE(data = Crow, measurevar = "Duration"
                     , groupvars = c("G.Env", "Behavior", "Sentinel"))
DurDot<-ggplot(data = MeanDur
               , aes(x = Behavior
                     , y = Duration
                     , color = Behavior
                     , shape = Sentinel))+
  geom_point(position = position_dodge2(width = 0.9)
             , size = 3) +
  geom_errorbar(aes(ymin=(Duration-se)
                    , ymax=(Duration+se))
                , width = 0.2
                , position = position_dodge(width=0.9))+
  theme_classic() +
  ylab("Mean Bout Duration (s)") +
  scale_colour_manual(values = cbPalette
                      , guide="none") +
  scale_shape_manual(values = c(16,17)
                     , labels = c("Sentinel Absent"
                                  , "Sentinel Present")) +
  scale_x_discrete(labels = c("Foraging", "Alert", "Moving"))+
  theme(axis.title.x = element_blank()
        , legend.position = "bottom"
        , legend.box="vertical"
        , legend.margin=margin()) +
  facet_grid(~G.Env)

@@

@@

```{r Duration Better Summary, echo = F}
sjPlot::tab_model(RLMM.Dur.I
                  , show.re.var = T
                  , title = "Model Results with Interactions"
                  , dv.labels = " Effects of on duration of behaviors"
                  , file="Tab_Dur_Model.html")

@@

```{r Proportion setup, include = F}
DATA<-read.csv("DATA.csv", stringsAsFactors = T)
DATA$ID<-as.factor(DATA$ID)
DATA$ASIN_PROPORTION<-asin(sqrt(DATA$BEHAVIOR_PROPORTION))
```

@@

>Let's run another PCA

```{r DATA PCA SHEET, include=F}
PCA.DATA.SHEET<-DATA[,c(5,7,10,14,16,18,22,23,24,39)]
head(PCA.DATA.SHEET)
str(PCA.DATA.SHEET)
```
```{R DATA PCA, echo=F}
PCA.DATA<-PCA(PCA.DATA.SHEET[,c(-8,-9)])
```

>There are many variables here. I won't bother describing them here.

>Since the presence of a sentinel is not "God-Given", we'll run another PCA without that factor.

```{r DATA PCA NO SENTINEL, echo=F}
PCA.DATA.NOSENT<-PCA(PCA.DATA.SHEET[,c(-5,-8,-9)])
```

>Very similar to the one above.

### Scree Plot

```{r DATA PCA Scree Plot, echo = F}
get_eigenvalue(PCA.DATA)
fviz_eig(PCA.DATA, addlabels=T, ylim = c(0,40))
```

>The first PC covers ~40% of the variation. The first 4 PCs cover ~82% of the variation.

```{r DATA PCA Scree Plot NO SENTINEL, echo = F}
get_eigenvalue(PCA.DATA.NOSENT)
fviz_eig(PCA.DATA.NOSENT, addlabels=T, ylim = c(0,40))
```

>Excluding sentinel, the first PC covers ~43% of the variation, and the first 4 PCs cover ~86% of the total variation.

### Contribution of variables to Principal Components

```{r PCA DATA var results, include = F}
DATA.var<-get_pca_var(PCA.DATA)
DATA.NOSENT.var<-get_pca_var(PCA.DATA.NOSENT)
```
```{r PCA DATA Contribution Dim 1, echo=F}
fviz_contrib(PCA.DATA, choice="var", axes = 1, top = 12.5)
```

>Very weird, Julian Date, Decimal time, group size and generalized environment contribute greatly to PC1.

```{r PCA DATA Contribution Dim 2, echo=F}
fviz_contrib(PCA.DATA, choice="var", axes = 2, top = 12.5)
```

>Frequency of disturbances, group size (again), temperature and the presence of a sentinel contribute most to PC2.

```{r PCA DATA Contribution Dim 3, echo=F}
fviz_contrib(PCA.DATA, choice="var", axes = 3, top = 12.5)
```

>Temperature, Bait presence and decimal time contribute most to PC3.

```{r PCA DATA Contribution Dim 4, echo=F}
fviz_contrib(PCA.DATA, choice="var", axes = 4, top = 12.5)
```

>Sentinel presence, environment and frequency of disturbances contribute most to PC4.

>I'm still a little unclear as to how I should interpret these results.

#### No Sentinel

```{r PCA DATA.NOSENT Contribution Dim 1, echo=F}
fviz_contrib(PCA.DATA.NOSENT, choice="var", axes = 1, top = 14.29)
```

>Same 4 factors contribute the most to PC1 in the absence of the sentinel factor.

```{r PCA DATA.NOSENT Contribution Dim 2, echo=F}
fviz_contrib(PCA.DATA.NOSENT, choice="var", axes = 2, top = 14.29)
```

>Same as above, frequency of disturbances, temperature and group size contribute most to PC2 in the absence of the sentinel factor.

```{r PCA DATA.NOSENT Contribution Dim 3, echo=F}
fviz_contrib(PCA.DATA.NOSENT, choice="var", axes = 3, top = 14.29)
```

>Temperature, Bait presence and frequency of disturbances contribute the most to PC3 in the absence of a sentinel.

```{r PCA DATA.NOSENT Contribution Dim 4, echo=F}
fviz_contrib(PCA.DATA.NOSENT, choice="var", axes = 4, top = 14.29)
```

>Environment contributes most to PC4 in the absence of a sentinel.

### BiPlots
```{r DATA PCA Biplot PC1-2, echo=F}
fviz_pca_biplot(PCA.DATA
                ,geom.ind = "point"
                , repel = T
                , col.ind=PCA.DATA.SHEET$BEHAVIOR
                , addEllipses = T
                , label = "var"
                , palette=cbPalette
                , col.var="black"
                , legend.title = "Behavior")
```

>Messy, can't see where the behaviors lie.

```{r DATA PCA Biplot PC1-4, echo=F}
fviz_pca_biplot(PCA.DATA
                , axes = c(1,4)
                , geom.ind = "point"
                , repel = T
                , col.ind=PCA.DATA.SHEET$BEHAVIOR
                , addEllipses = T
                , label = "var"
                , palette=cbPalette
                , col.var="black"
                , legend.title = "Behavior")
```

>Still messy.

```{r DATA PCA Biplot PC2-3, echo=F}
fviz_pca_biplot(PCA.DATA
                , axes = c(2,3)
                , geom.ind = "point"
                , repel = T
                , col.ind=PCA.DATA.SHEET$BEHAVIOR
                , addEllipses = T
                , label = "var"
                , palette=cbPalette
                , col.var="black"
                , legend.title = "Behavior")
```

>Biplots are messy if we don't include behavior.

>Same is observed if we run the biplot in the absence of the sentinel factor.

>I'm not sure how to interpret these results.

@@

>>>>

```{r DATA setup, include = F}
DATA<-read.csv("DATA.csv", stringsAsFactors = T)
DATA<-DATA[,c(-3,-4,-6)]
DATA$ID<-as.factor(DATA$ID)
DATA$LOG_DURATION<-log(DATA$MEAN_BOUT_DURATION)
DATA$LOG_DURATION[is.infinite(DATA$LOG_DURATION)]<-NA
DATA$ASIN_PROPORTION<-asin(sqrt(DATA$BEHAVIOR_PROPORTION))

@@

```{r Duration Histograms Individual, include = F}
Untransformed.Dur<-hist(DATA$MEAN_BOUT_DURATION, breaks = 25)
Transformed.Dur<-hist(DATA$LOG_DURATION, breaks = 25)
```

@@

```{r Crow Histogram, echo=F}
Hist<-ggplot(data = DATA) +
  geom_histogram(aes(fill = BEHAVIOR, x = LOG_DURATION)
                 , alpha = 1
                 , bins = 50)+
  scale_fill_manual(values=cbPalette
                    , labels = c("Foraging", "Alert", "Moving"))+
  xlab("Log Duration (s)")+
  ylab("Count")
Hist
```

@@

<!-- ### Boxplot -->

<!-- ```{r Crow boxplot, echo = F} -->
<!-- Box<-ggplot(data = Crow)+ -->
<!--   geom_boxplot_pattern(aes(x = G.Env, y = LDur, fill = Behavior, pattern = Sentinel) -->
<!--                        , pattern_angle = 45 -->
<!--                        , pattern_size = 0.05 -->
<!--                        , pattern_spacing = 0.02 -->
<!--                        , color = "black")+ -->
<!--   theme(legend.position = "bottom")+ -->
<!--   scale_fill_manual(values = cbPalette -->
<!--                     , labels = c("Foraging", "Alert", "Moving"))+ -->
<!--   scale_pattern_manual(values = c("crosshatch", "none") -->
<!--                        , labels = c("Sentinel Absent", "Sentinel Present"))+ -->
<!--   guides(pattern = guide_legend(title = "Presence of a sentinel" -->
<!--                                 , override.aes = list(fill = c("white"))) -->
<!--          , fill = guide_legend(override.aes = list(pattern = "none")))+ -->
<!--   xlab("Generalized Environment")+ -->
<!--   ylab("Log Duration(s)") + -->
<!--   theme(axis.title.x = element_blank() -->
<!--         , legend.position = "bottom" -->
<!--         , legend.box="vertical" -->
<!--         , legend.margin=margin()) -->
<!-- Box -->
<!-- ``` -->

<!-- ### Violin plot -->

<!-- ```{r Crow Violin plot, echo = F} -->
<!-- Violin<-ggplot(data = Crow -->
<!--                , aes(x = Behavior, y = LDur, fill = Sentinel))+ -->
<!--   geom_violin()+ -->
<!--   theme_bw()+ -->
<!--   theme(legend.position = "bottom")+ -->
<!--   scale_fill_manual(values = cbPalette -->
<!--                     , labels = c("Sentinel Absent", "Sentinel Present"))+ -->
<!--   scale_x_discrete(labels=c("Foraging", "Alert", "Moving"))+ -->
<!--   xlab("Generalized Environment")+ -->
<!--   ylab("Log Duration(s)")+ -->
<!--   facet_grid(~G.Env)+ -->
<!--   stat_summary(fun = "mean" -->
<!--                , geom = "crossbar" -->
<!--                , position = "dodge" -->
<!--                , color = "red") -->
<!-- Violin -->
<!-- ``` -->

<!-- >These plots are nice, but it is hard to really see the underlying trends. To best visualise them, I'll next plot a dot plot. -->

@@

<!-- ```{r Base R Plot, include = F} -->
<!-- source("./Calculate Summary Table with SE, SD, CI by grouping variables.R") -->
<!-- MeanDur <- summarySE(data = Crow, measurevar = "Duration" -->
<!--                      , groupvars = c("G.Env", "Behavior", "Sentinel")) -->

<!-- plot(x = c(1:12) -->
<!--      , y = MeanDur$Duration -->
<!--      , xlim = c(0,12) -->
<!--      , ylim = c(1,3) -->
<!--      , type = "n" -->
<!--      , ylab = "Duration (seconds)", xlab = "Generalized Environment") -->
<!-- arrows(c(1:12), MeanDur$Duration - MeanDur$se -->
<!--        , c(1:12), MeanDur$Duration + MeanDur$se -->
<!--        , length = 0.1, angle = 90, code = 3, lwd = 2) -->
<!-- points(x = c(1:12), y = MeanDur$Duration -->
<!--        , pch = c(rep(c(16, 17), 3)), cex = 2 -->
<!--        , col = c("orange", "orange", "blue", "blue", "green", "green")) -->
<!-- legend(x = "bottomright", c("Sentinel Absent", "Sentinal Present", "Foraging", "Alert", "Moving") -->
<!--        , bty = "o", cex = 1.05, bg = "white" -->
<!--        , pch = c(16, 17, 15, 15, 15), col = c("black", "black", "orange", "blue", "green")) -->
<!-- #KMG: I'm not going to fix the X-axis labels and those kinds of things right now. I can do that if you like this plot or things it's informative. I think it's easier to see the differences. left side is commercial, right side is green. Legend should be correct. -->
<!-- ``` -->

```{r Dot Plot V2, echo = F}
source("./Calculate Summary Table with SE, SD, CI by grouping variables.R")
MeanDur <- summarySE(data = DATA, measurevar = "MEAN_BOUT_DURATION"
                     , groupvars = c("GENERALIZED_ENVIRONMENT", "BEHAVIOR", "SENTINEL_PRESENCE"))
DurDot<-ggplot(data = MeanDur
               , aes(x = BEHAVIOR
                     , y = MEAN_BOUT_DURATION
                     , color = BEHAVIOR
                     , shape = SENTINEL_PRESENCE))+
  geom_point(position = position_dodge2(width = 0.9)
             , size = 3) +
  geom_errorbar(aes(ymin=(MEAN_BOUT_DURATION-se)
                    , ymax=(MEAN_BOUT_DURATION+se))
                , width = 0.2
                , position = position_dodge(width=0.9))+
  theme_classic() +
  ylab("Mean Bout Duration (s)") +
  scale_colour_manual(values = cbPalette
                      , guide="none") +
  scale_shape_manual(values = c(16,17)
                     , labels = c("Sentinel Absent"
                                  , "Sentinel Present")) +
  scale_x_discrete(labels = c("Foraging", "Alert", "Moving"))+
  theme(axis.title.x = element_blank()
        , legend.position = "bottom"
        , legend.box="vertical"
        , legend.margin=margin()) +
  facet_grid(~GENERALIZED_ENVIRONMENT)

@@

```{r DATA Duration RLMM, echo=F}
RLMM.Dur.DATA<-rlmer(LOG_DURATION~BEHAVIOR+SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT+SENTINEL_PRESENCE*GROUP_SIZE+BAIT_PRESENCE+SENTINEL_PRESENCE+GENERALIZED_ENVIRONMENT+(1|ID), data = DATA)
plot(RLMM.Dur.DATA)
```

@@

```{r Duration Better Summary, echo = F}
sjPlot::tab_model(RLMM.Dur.DATA
                  , show.re.var = T
                  , title = "Model Results with Interactions"
                  , dv.labels = " Effects of on duration of behaviors")

@@

@@

<!-- >Let's run another PCA -->

<!-- ```{r DATA PCA SHEET, include=F} -->
<!-- PCA.DATA.SHEET<-DATA[,c(5,7,10,14,16,18,22,23,24,39)] -->
<!-- head(PCA.DATA.SHEET) -->
<!-- str(PCA.DATA.SHEET) -->
<!-- ``` -->
<!-- ```{R DATA PCA, echo=F} -->
<!-- PCA.DATA<-PCA(PCA.DATA.SHEET[,c(-8,-9)]) -->
<!-- ``` -->

<!-- >There are many variables here. I won't bother describing them here. -->

<!-- >Since the presence of a sentinel is not "God-Given", we'll run another PCA without that factor. -->

<!-- ```{r DATA PCA NO SENTINEL, echo=F} -->
<!-- PCA.DATA.NOSENT<-PCA(PCA.DATA.SHEET[,c(-5,-8,-9)]) -->
<!-- ``` -->

<!-- >Very similar to the one above. -->

<!-- ### Scree Plot -->

<!-- ```{r DATA PCA Scree Plot, echo = F} -->
<!-- get_eigenvalue(PCA.DATA) -->
<!-- fviz_eig(PCA.DATA, addlabels=T, ylim = c(0,40)) -->
<!-- ``` -->

<!-- >The first PC covers ~40% of the variation. The first 4 PCs cover ~82% of the variation. -->

<!-- ```{r DATA PCA Scree Plot NO SENTINEL, echo = F} -->
<!-- get_eigenvalue(PCA.DATA.NOSENT) -->
<!-- fviz_eig(PCA.DATA.NOSENT, addlabels=T, ylim = c(0,40)) -->
<!-- ``` -->

<!-- >Excluding sentinel, the first PC covers ~43% of the variation, and the first 4 PCs cover ~86% of the total variation. -->

<!-- ### Contribution of variables to Principal Components -->

<!-- ```{r PCA DATA var results, include = F} -->
<!-- DATA.var<-get_pca_var(PCA.DATA) -->
<!-- DATA.NOSENT.var<-get_pca_var(PCA.DATA.NOSENT) -->
<!-- ``` -->
<!-- ```{r PCA DATA Contribution Dim 1, echo=F} -->
<!-- fviz_contrib(PCA.DATA, choice="var", axes = 1, top = 12.5) -->
<!-- ``` -->

<!-- >Very weird, Julian Date, Decimal time, group size and generalized environment contribute greatly to PC1. -->

<!-- ```{r PCA DATA Contribution Dim 2, echo=F} -->
<!-- fviz_contrib(PCA.DATA, choice="var", axes = 2, top = 12.5) -->
<!-- ``` -->

<!-- >Frequency of disturbances, group size (again), temperature and the presence of a sentinel contribute most to PC2. -->

<!-- ```{r PCA DATA Contribution Dim 3, echo=F} -->
<!-- fviz_contrib(PCA.DATA, choice="var", axes = 3, top = 12.5) -->
<!-- ``` -->

<!-- >Temperature, Bait presence and decimal time contribute most to PC3. -->

<!-- ```{r PCA DATA Contribution Dim 4, echo=F} -->
<!-- fviz_contrib(PCA.DATA, choice="var", axes = 4, top = 12.5) -->
<!-- ``` -->

<!-- >Sentinel presence, environment and frequency of disturbances contribute most to PC4. -->

<!-- >I'm still a little unclear as to how I should interpret these results. -->

<!-- #### No Sentinel -->

<!-- ```{r PCA DATA.NOSENT Contribution Dim 1, echo=F} -->
<!-- fviz_contrib(PCA.DATA.NOSENT, choice="var", axes = 1, top = 14.29) -->
<!-- ``` -->

<!-- >Same 4 factors contribute the most to PC1 in the absence of the sentinel factor. -->

<!-- ```{r PCA DATA.NOSENT Contribution Dim 2, echo=F} -->
<!-- fviz_contrib(PCA.DATA.NOSENT, choice="var", axes = 2, top = 14.29) -->
<!-- ``` -->

<!-- >Same as above, frequency of disturbances, temperature and group size contribute most to PC2 in the absence of the sentinel factor. -->

<!-- ```{r PCA DATA.NOSENT Contribution Dim 3, echo=F} -->
<!-- fviz_contrib(PCA.DATA.NOSENT, choice="var", axes = 3, top = 14.29) -->
<!-- ``` -->

<!-- >Temperature, Bait presence and frequency of disturbances contribute the most to PC3 in the absence of a sentinel. -->

<!-- ```{r PCA DATA.NOSENT Contribution Dim 4, echo=F} -->
<!-- fviz_contrib(PCA.DATA.NOSENT, choice="var", axes = 4, top = 14.29) -->
<!-- ``` -->

<!-- >Environment contributes most to PC4 in the absence of a sentinel. -->

<!-- ### BiPlots -->
<!-- ```{r DATA PCA Biplot PC1-2, echo=F} -->
<!-- fviz_pca_biplot(PCA.DATA -->
<!--                 ,geom.ind = "point" -->
<!--                 , repel = T -->
<!--                 , col.ind=PCA.DATA.SHEET$BEHAVIOR -->
<!--                 , addEllipses = T -->
<!--                 , label = "var" -->
<!--                 , palette=cbPalette -->
<!--                 , col.var="black" -->
<!--                 , legend.title = "Behavior") -->
<!-- ``` -->

<!-- >Messy, can't see where the behaviors lie. -->

<!-- ```{r DATA PCA Biplot PC1-4, echo=F} -->
<!-- fviz_pca_biplot(PCA.DATA -->
<!--                 , axes = c(1,4) -->
<!--                 , geom.ind = "point" -->
<!--                 , repel = T -->
<!--                 , col.ind=PCA.DATA.SHEET$BEHAVIOR -->
<!--                 , addEllipses = T -->
<!--                 , label = "var" -->
<!--                 , palette=cbPalette -->
<!--                 , col.var="black" -->
<!--                 , legend.title = "Behavior") -->
<!-- ``` -->

<!-- >Still messy. -->

<!-- ```{r DATA PCA Biplot PC2-3, echo=F} -->
<!-- fviz_pca_biplot(PCA.DATA -->
<!--                 , axes = c(2,3) -->
<!--                 , geom.ind = "point" -->
<!--                 , repel = T -->
<!--                 , col.ind=PCA.DATA.SHEET$BEHAVIOR -->
<!--                 , addEllipses = T -->
<!--                 , label = "var" -->
<!--                 , palette=cbPalette -->
<!--                 , col.var="black" -->
<!--                 , legend.title = "Behavior") -->
<!-- ``` -->

<!-- >Biplots are messy if we don't include behavior. -->

<!-- >Same is observed if we run the biplot in the absence of the sentinel factor. -->

<!-- >I'm not sure how to interpret these results. -->

@@

# Sentinel Presence

I'll try to use a correlation test to determine if the presence of a sentinel (Yes/No, binary data) is correlated with the type of environment, the frequency of disturbances and the group size.

```{r Correlation test}
cor(DATA[, c("CODED_SENTINEL_PRESENCE", "CODED_ENV", "CODED_GROUP_SIZE", "TOTAL_FREQUENCY_OF_DISTURBANCES")])
```
